Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-13 tex/VHzQ.tex
updated Abstract

The clipped median and median absolute deviation is then calculated
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, m.a.d. is the median absolute
deviation, and $\bar{\epsilon}$ is the mean of the error in each point
in the light curve, divided by the total number of points. We apply the criteria 
$var>=3.$ to light-curves from the original measurements and also to light-curves 
where measurements have been averaged over different time-scales to improve 
the signal-to-noise. We found that two quasars showed signs of variability:
MMT J0215-0529 in the Y-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
SDSS J0959+0227 in the Y and H bands, with timescales of 1 year or 6 months 
for Y only. The H-band amplitude was 0.9 mag and the Y-band amplitude was 1.2 mag if averaged over 6 months,
or 0.9 mag if averaged over 1 year.

>>>>

The clipped median and median absolute deviation is then calculated
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, m.a.d. is the median absolute
deviation, and $\bar{\epsilon}$ is the mean of the error in each point
in the light curve, divided by the total number of points. We apply the criteria 
$var>=3.$ to light-curves from the original measurements and also to light-curves 
where measurements have been averaged over different time-scales to improve 
the signal-to-noise. We found that two quasars showed signs of variability:
MMT J0215-0529 in the $Y$-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
SDSS J0959+0227 in the $Y$ and $H$-bands, with timescales of 1 year or 6 months 
for $Y$ only. The $H$-band amplitude was 0.9 mag and the $Y$-band amplitude was 1.2 mag if averaged over 6 months,
or 0.9 mag if averaged over 1 year.
